Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2013-01-22 text/paper/paper3.tex
polished plots and fixed table order in appendix

\begin{figure}
\includegraphics[width=\textwidth]{../pictures/paper/graph_ec.pdf}
\caption{Judgments for prefence-related controls (EC sequence). Relative frequencies
of {\it yes/no} judgments is plotted against the position within the
trial. Each {\it EC sequences} consisted of five pictures, in which the
critical positions for a reading were the third position ("false" corresponded
to an \ec reading) and the fifth position ("true" corresponded to an \lc reading)}
\label{Fig:EC_judgments}
\end{figure}

%\clearpage

\begin{figure}
\includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
\caption{Judgments for prefence-related controls (LC sequence). Relative frequencies
of {\it yes/no} judgments is plotted against the position within the
trial. Each {\it LC sequences} consisted of seven pictures, in which the
critical positions for a reading were the third position ("true" corresponded
to an \lc reading) and the sixth position ("false" corresponded to an \ec reading).}
\label{Fig:LC_judgments}
\end{figure}

@@

@@

\begin{table}
  \centering

>>>>

\begin{figure}[]
\centering
\subfloat[][neutral accentuation]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
\begin{tikzpicture}[scale=0.8]

      \begin{axis}[ybar, 
                  enlarge x limits=0.2,
                  enlarge y limits=0.1,
                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
                  ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,64)};

        \addplot coordinates {(1,4) (2,2) (3,26) (4,1) (5,5)};

      \end{axis}
\end{tikzpicture}
% \label{fig:ReadingsAS-ntr}
}
\subfloat[][prosody cues \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
\begin{tikzpicture}[scale=0.8]

        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,76)};

        \addplot coordinates {(1,4) (2,0) (3,13) (4,2) (5,5)};

        % \legend{yes, no}

\subfloat[][prosody cues \ec-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
\begin{tikzpicture}[scale=0.8]

      \begin{axis}[ybar, 
                  enlarge x limits=0.2,
                  enlarge y limits=0.1,
                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
                  ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,56)};

        \addplot coordinates {(1,2) (2,1) (3,33) (4,2) (5,6)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsAS-acc}
}
\subfloat[][unambiguous \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
\begin{tikzpicture}[scale=0.8]

        \addplot coordinates {(1,1) (2,0) (3,0) (4,1) (5,86)};

        \addplot coordinates {(1,6) (2,0) (3,5) (4,0) (5,2)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsES-acc}
}
% \includegraphics[width=\textwidth]{../pictures/paper/graph_ec.pdf}
\caption{Judgments for preference-related controls (EC
  sequence). Rounded percentages of {\it yes/no} judgments are plotted
  against the position within the trial. Each EC sequence consisted of
  five pictures, in which the critical positions for a reading were
  the third position (\emph{no} corresponded to an \ec reading) and
  the fifth position (\emph{yes} corresponded to an \lc reading).}
\label{Fig:EC_judgments}
\end{figure}

\begin{figure}[]
\centering
\subfloat[][neutral accentuation]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
\begin{tikzpicture}[scale=0.8]

        \addplot coordinates {(1,0) (2,0) (3,68) (4,0) (5,0) (6,1) (7,0)};

        \addplot coordinates {(1,0) (2,0) (3,5) (4,0) (5,0) (6,25) (7,2)};

      \end{axis}
\end{tikzpicture}
% \label{fig:ReadingsAS-ntr}
}
\subfloat[][prosody cues \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
\begin{tikzpicture}[scale=0.8]

      \begin{axis}[ybar, 
                  enlarge x limits=0.1,
                  enlarge y limits=0.1,
                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
                  % ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,79) (4,1) (5,1) (6,2) (7,1)};

        \addplot coordinates {(1,0) (2,1) (3,3) (4,0) (5,0) (6,13) (7,0)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsES-ntr}
}

\subfloat[][prosody cues \ec-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
\begin{tikzpicture}[scale=0.8]

        \addplot coordinates {(1,0) (2,0) (3,51) (4,2) (5,1) (6,4) (7,0)};

        \addplot coordinates {(1,2) (2,0) (3,8) (4,1) (5,0) (6,30) (7,2)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsAS-acc}
}
\subfloat[][unambiguous \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
\begin{tikzpicture}[scale=0.8]

      \begin{axis}[ybar, 
                  enlarge x limits=0.1,
                  enlarge y limits=0.1,
                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
                  % ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,88) (4,2) (5,0) (6,5) (7,0)};

        \addplot coordinates {(1,1) (2,0) (3,1) (4,0) (5,0) (6,3) (7,0)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsES-acc}
}
% \includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
\caption{Judgments for preference-related controls (LC
  sequence). Rounded percentages of {\it yes/no} judgments are plotted
  against the position within the trial. Each LC sequence consisted of
  seven pictures, in which the critical positions for a reading were
  the third position (\emph{yes} corresponded to an \lc reading) and the
  sixth position (\emph{no} corresponded to an \ec reading).}
\label{Fig:LC_judgments}
\end{figure}

@@

\newpage

@@

\begin{table}[!hp]
  \centering
